Comparison of Catalogs

### 2024-07-31 compare/compare.qmd
Stellar Masses

@@

```{python}
# Create a pair grid
sns.pairplot(mass_data, corner=True)
plt.show()
```
:::

>>>>

::: panel-tabset
## Stellar Masses Comparison

dt["diff_M"] =  relative_diff(hec = dt["logM_HEC"].data, lcv = dt["logStellarMass"])
temp = dt[["diff_M"]].to_pandas()
sns.histplot(temp, kde = True)
plt.title("Percentage change Distribution [%]")
plt.xlabel(r"$\log_{10}M_*$ "+f"[{dt['logM_HEC'].unit}]")
plt.show()

```{python}
temp.rename(columns={"diff_M":"Percantage Change [%]"}, inplace = True)
```
```{python}
temp.describe()
```
## Heatmap

@@

```{python}
# Create a pair grid
sns.pairplot(mass_data, corner=True)
plt.show()
```

## Density Grid

```{python}
# Create a pair grid
sns.pairplot(mass_data, corner=True, kind="kde", diag_kind="hist")
plt.show()
```
:::
